---
title: "Tampa Bay Rays R&D"
output: html_document
author: "Dylan Zumar (Duke University Class of 2021)"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r, include=FALSE}
library("dplyr")
library("ggplot2")
library("cowplot")
library("knitr")
library("broom")
```

```{r}
dataset <- read.csv("battedBallData.csv")
dataset %>%
  group_by(hittype) %>%
  summarise(count = n())
dataset <- dataset %>%
  filter(hittype != "U")
```

There were two instances in the data set where the hit type was 'U' (presumably "unknown"), which I removed from the data set since there is likely little information to be gleaned from those two cases.

## Exploratory Data Analysis

# Creating Boxplots of Speed and Angles for each Hit Type

In order to tell the differences between system A and system B, I will make boxplots for the angles and speeds measured by A and B split up for each hit type. This will hopefully isolate the flaws in A and B.

```{r}
speedAgb <- dataset %>%
  filter(hittype == "ground_ball") %>%
  ggplot(mapping = aes(y = speed_A)) +
  geom_boxplot()
speedAld <- dataset %>%
  filter(hittype == "line_drive") %>%
  ggplot(mapping = aes(y = speed_A)) +
  geom_boxplot()
speedAfb <- dataset %>%
  filter(hittype == "fly_ball") %>%
  ggplot(mapping = aes(y = speed_A)) +
  geom_boxplot()
speedApu <- dataset %>%
  filter(hittype == "popup") %>%
  ggplot(mapping = aes(y = speed_A)) +
  geom_boxplot()
```

```{r}
vangleAgb <- dataset %>%
  filter(hittype == "ground_ball") %>%
  ggplot(mapping = aes(y = vangle_A)) +
  geom_boxplot()
vangleAld <- dataset %>%
  filter(hittype == "line_drive") %>%
  ggplot(mapping = aes(y = vangle_A)) +
  geom_boxplot()
vangleAfb <- dataset %>%
  filter(hittype == "fly_ball") %>%
  ggplot(mapping = aes(y = vangle_A)) +
  geom_boxplot()
vangleApu <- dataset %>%
  filter(hittype == "popup") %>%
  ggplot(mapping = aes(y = vangle_A)) +
  geom_boxplot()
```

```{r}
speedBgb <- dataset %>%
  filter(hittype == "ground_ball") %>%
  ggplot(mapping = aes(y = speed_B)) +
  geom_boxplot()
speedBld <- dataset %>%
  filter(hittype == "line_drive") %>%
  ggplot(mapping = aes(y = speed_B)) +
  geom_boxplot()
speedBfb <- dataset %>%
  filter(hittype == "fly_ball") %>%
  ggplot(mapping = aes(y = speed_B)) +
  geom_boxplot()
speedBpu <- dataset %>%
  filter(hittype == "popup") %>%
  ggplot(mapping = aes(y = speed_B)) +
  geom_boxplot()
```

```{r}
vangleBgb <- dataset %>%
  filter(hittype == "ground_ball") %>%
  ggplot(mapping = aes(y = vangle_B)) +
  geom_boxplot()
vangleBld <- dataset %>%
  filter(hittype == "line_drive") %>%
  ggplot(mapping = aes(y = vangle_B)) +
  geom_boxplot()
vangleBfb <- dataset %>%
  filter(hittype == "fly_ball") %>%
  ggplot(mapping = aes(y = vangle_B)) +
  geom_boxplot()
vangleBpu <- dataset %>%
  filter(hittype == "popup") %>%
  ggplot(mapping = aes(y = vangle_B)) +
  geom_boxplot()
```

# Displaying Boxplots Side-by-Side with 5-Number Summary

## Ground balls
```{r}
plot_grid(speedAgb, speedBgb)
dataset %>%
  filter(hittype == "ground_ball") %>%
  summarise(minA = min(speed_A, na.rm = TRUE), q1A = quantile(speed_A, 0.25, na.rm = TRUE), 
            meanA = mean(speed_A, na.rm = TRUE), q3A = quantile(speed_A, 0.75, na.rm = TRUE),
            maxA = max(speed_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "ground_ball") %>%
  summarise(minB = min(speed_B, na.rm = TRUE), q1B = quantile(speed_B, 0.25, na.rm = TRUE), 
            meanB = mean(speed_B, na.rm = TRUE), q3B = quantile(speed_B, 0.75, na.rm = TRUE),
            maxB = max(speed_B, na.rm = TRUE))

plot_grid(vangleAgb, vangleBgb)
dataset %>%
  filter(hittype == "ground_ball") %>%
  summarise(minA = min(vangle_A, na.rm = TRUE), q1A = quantile(vangle_A, 0.25, na.rm = TRUE),
            meanA = mean(vangle_A, na.rm = TRUE), q3A = quantile(vangle_A, 0.75, na.rm = TRUE),
            maxA = max(vangle_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "ground_ball") %>%
  summarise(minB = min(vangle_B, na.rm = TRUE), q1B = quantile(vangle_B, 0.25, na.rm = TRUE),
            meanB = mean(vangle_B, na.rm = TRUE), q3B = quantile(vangle_B, 0.75, na.rm = TRUE),
            maxB = max(vangle_B, na.rm = TRUE))

ttestspeedAgb <- as.data.frame(dataset %>% 
  filter(hittype == "ground_ball") %>% 
  select(speed_A))
ttestspeedBgb <- as.data.frame(dataset %>% 
  filter(hittype == "ground_ball") %>% 
  select(speed_B))
t.test(ttestspeedAgb, ttestspeedBgb, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)

ttestvangleAgb <- as.data.frame(dataset %>% 
  filter(hittype == "ground_ball") %>% 
  select(vangle_A))
ttestvangleBgb <- as.data.frame(dataset %>% 
  filter(hittype == "ground_ball") %>% 
  select(vangle_B))
t.test(ttestvangleAgb, ttestvangleBgb, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```

We can see that the distribution for the speed calculated by system A for ground balls is very different from the distribution for the speed calculated by system B. However, the angles calculated from the two systems are similar. Given that system A is suspected to be more accurate than system B, it appears that the speed for ground balls should be calculated using system A.


## Line drives
```{r}
plot_grid(speedAld, speedBld)
dataset %>%
  filter(hittype == "line_drive") %>%
  summarise(minA = min(speed_A, na.rm = TRUE), q1A = quantile(speed_A, 0.25, na.rm = TRUE), meanA
            = mean(speed_A, na.rm = TRUE), q3A = quantile(speed_A, 0.75, na.rm = TRUE), maxA =
              max(speed_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "line_drive") %>%
  summarise(minB = min(speed_B, na.rm = TRUE), q1B = quantile(speed_B, 0.25, na.rm = TRUE), meanB
            = mean(speed_B, na.rm = TRUE), q3B = quantile(speed_B, 0.75, na.rm = TRUE), maxB =
              max(speed_B, na.rm = TRUE))

plot_grid(vangleAld, vangleBld)
dataset %>%
  filter(hittype == "line_drive") %>%
  summarise(minA = min(vangle_A, na.rm = TRUE), q1A = quantile(vangle_A, 0.25, na.rm = TRUE),
            meanA = mean(vangle_A, na.rm = TRUE), q3A = quantile(vangle_A, 0.75, na.rm = TRUE),
            maxA = max(vangle_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "line_drive") %>%
  summarise(minB = min(vangle_B, na.rm = TRUE), q1B = quantile(vangle_B, 0.25, na.rm = TRUE),
            meanB = mean(vangle_B, na.rm = TRUE), q3B = quantile(vangle_B, 0.75, na.rm = TRUE),
            maxB = max(vangle_B, na.rm = TRUE))

ttestspeedAld <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_A))
ttestspeedBld <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_B))
t.test(ttestspeedAld, ttestspeedBld, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)

ttestvangleAld <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_A))
ttestvangleBld <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_B))
t.test(ttestvangleAld, ttestvangleBld, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```

The distributions for speed and angle for line drives appear to be more or less the same for system A and system B. However, the negative angles for line drives are very unusual and unintuitive, and they should perhaps be cleaned from the data set. Alternatively, if an angle measurement for A is negative but is positive for B, then B should be used (and vice versa).


## Fly balls
```{r}
plot_grid(speedAfb, speedBfb)
dataset %>%
  filter(hittype == "fly_ball") %>%
  summarise(minA = min(speed_A, na.rm = TRUE), q1A = quantile(speed_A, 0.25, na.rm = TRUE), meanA
            = mean(speed_A, na.rm = TRUE), q3A = quantile(speed_A, 0.75, na.rm = TRUE), maxA =
              max(speed_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "fly_ball") %>%
  summarise(minB = min(speed_B, na.rm = TRUE), q1B = quantile(speed_B, 0.25, na.rm = TRUE), meanB
            = mean(speed_B, na.rm = TRUE), q3B = quantile(speed_B, 0.75, na.rm = TRUE), maxB =
              max(speed_B, na.rm = TRUE))
  
plot_grid(vangleAfb, vangleBfb)
dataset %>%
  filter(hittype == "fly_ball") %>%
  summarise(minA = min(vangle_A, na.rm = TRUE), q1A = quantile(vangle_A, 0.25, na.rm = TRUE),
            meanA = mean(vangle_A, na.rm = TRUE), q3A = quantile(vangle_A, 0.75, na.rm = TRUE),
            maxA = max(vangle_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "fly_ball") %>%
  summarise(minB = min(vangle_B, na.rm = TRUE), q1B = quantile(vangle_B, 0.25, na.rm = TRUE),
            meanB = mean(vangle_B, na.rm = TRUE), q3B = quantile(vangle_B, 0.75, na.rm = TRUE),
            maxB = max(vangle_B, na.rm = TRUE))

ttestspeedAfb <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_A))
ttestspeedBfb <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_B))
t.test(ttestspeedAfb, ttestspeedBfb, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)

ttestvangleAfb <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_A))
ttestvangleBfb <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_B))
t.test(ttestvangleAfb, ttestvangleBfb, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```

Again, the distributions appear to be similar for fly balls; however, the `vangle` outliers for system A are much more significant and should be cleaned from the data set. 

## Pop ups
```{r}
plot_grid(speedApu, speedBpu)
dataset %>%
  filter(hittype == "popup") %>%
  summarise(minA = min(speed_A, na.rm = TRUE), q1A = quantile(speed_A, 0.25, na.rm = TRUE), meanA
            = mean(speed_A, na.rm = TRUE), q3A = quantile(speed_A, 0.75, na.rm = TRUE), maxA =
              max(speed_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "popup") %>%
  summarise(minB = min(speed_B, na.rm = TRUE), q1B = quantile(speed_B, 0.25, na.rm = TRUE), meanB
            = mean(speed_B, na.rm = TRUE), q3B = quantile(speed_B, 0.75, na.rm = TRUE), maxB =
              max(speed_B, na.rm = TRUE))


plot_grid(vangleApu, vangleBpu)
dataset %>%
  filter(hittype == "popup") %>%
  summarise(minA = min(vangle_A, na.rm = TRUE), q1A = quantile(vangle_A, 0.25, na.rm = TRUE),
            meanA = mean(vangle_A, na.rm = TRUE), q3A = quantile(vangle_A, 0.75, na.rm = TRUE),
            maxA = max(vangle_A, na.rm = TRUE))
dataset %>%
  filter(hittype == "popup") %>%
  summarise(minB = min(vangle_B, na.rm = TRUE), q1B = quantile(vangle_B, 0.25, na.rm = TRUE),
            meanB = mean(vangle_B, na.rm = TRUE), q3B = quantile(vangle_B, 0.75, na.rm = TRUE),
            maxB = max(vangle_B, na.rm = TRUE))

ttestspeedApu <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_A))
ttestspeedBpu <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(speed_B))
t.test(ttestspeedApu, ttestspeedBpu, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)

ttestvangleApu <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_A))
ttestvangleBpu <- as.data.frame(dataset %>% 
  filter(hittype == "line_drive") %>% 
  select(vangle_B))
t.test(ttestvangleApu, ttestvangleBpu, alternative = "two.sided", mu = 0, 
       paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```

The speeds from systems A and B appear to be more or less the same; however, the angles are distinctly different. Again, the heuristic in this case would be to trust A over B, though it is possible that the launch angle simply should not be used to predict speed for popups.

# Data Cleaning/Analysis

Since the t-tests for all of the above speeds/angles for each hit type provided little information, I will base the following on the results of the boxplots.

## Ground balls

For ground balls, we found that the speeds calculated by B were drastically different than those calculated by A. Since we are given that system A is assumed to be more accurate than system B, when system A is known, it should be used to predict the true speed for ground balls.

```{r}
dataset <- dataset %>%
  mutate(true_speed = case_when(
    is.na(speed_A) == TRUE ~ NA_real_,
    hittype == "ground_ball" ~ speed_A
  ))
```

When system A is NA for ground balls, our only option is to predict A using B. We will fit a linear regression using the speed and angle for B. Since the distribution of the angles for A and B appeared similar, it is likely that `vangle_B` is a good predictor of `speed_A`, but we will initially begin with `speed_B` and `vangle_B` as predictors.

```{r}
full_model_gb <- lm(data = subset(dataset, hittype == "ground_ball"), 
                    speed_A ~ speed_B + vangle_B + speed_B*vangle_B)
partial_model_gb <- lm(data = subset(dataset, hittype == "ground_ball"), 
                       speed_A ~ speed_B + vangle_B)
angle_model_gb <- lm(data = subset(dataset, hittype == "ground_ball"), speed_A ~ vangle_B)

kable(anova(partial_model_gb,full_model_gb,test="Chisq"),format="html")
summary(full_model_gb)$r.squared
summary(partial_model_gb)$r.squared
summary(angle_model_gb)$r.squared
```

The nested F test shows that that the full model is the best linear regression to predict `speed_A` from system B. The r-squared values confirm this, and it shows that simply using `vangle_B` is not an accurate way to predict `speed_A`. Finally, we will predict the `true_speed` of all ground balls by fitting the full model to ground ball cases where system A is NA.

```{r}
dataset <- dataset %>%
  mutate(speed_A = ifelse(is.na(speed_A) & hittype == "ground_ball", predict(full_model_gb), 
                          speed_A))
dataset <- dataset %>%
  mutate(true_speed = ifelse(is.na(true_speed) & hittype == "ground_ball", speed_A, true_speed))
```

## Line drives

For line drives, the distributions of speeds and angles for A and B appeared to be more or less similar. However, there were a number of angles that were calculated as negative, which does not make sense in the case of line drives. We will first look at the negative angle values for line drives and see if it is consistent between A and B to perform some data cleaning.

```{r, echo=FALSE}
#dataset %>%
  #filter(hittype == "line_drive" & vangle_A < 0)
#dataset %>%
  #filter(hittype == "line_drive" & vangle_B < 0)
dataset <- dataset %>%
  filter((hittype == "line_drive" & vangle_A < 0 & vangle_B < 0) == FALSE)
```

We removed all line drives that had negative angles recorded from both systems A and B because they, intuitively, do not qualify as line drives and should not be used to calculate true speed. Now, we will predict A from B and vice versa for the NAs.

```{r}
full_model_ld <- lm(data = subset(dataset, hittype == "line_drive"), 
                    speed_A ~ speed_B + vangle_B + speed_B*vangle_B)
partial_model_ld <- lm(data = subset(dataset, hittype == "line_drive"), 
                       speed_A ~ speed_B + vangle_B)
angle_model_ld <- lm(data = subset(dataset, hittype == "line_drive"), speed_A ~ vangle_B)

kable(anova(partial_model_ld,full_model_ld,test="Chisq"),format="html")
summary(full_model_ld)$r.squared
summary(partial_model_ld)$r.squared
summary(angle_model_ld)$r.squared

full_model_ldB <- lm(data = subset(dataset, hittype == "line_drive"), 
                    speed_B ~ speed_A + vangle_A + speed_A*vangle_A)
partial_model_ldB <- lm(data = subset(dataset, hittype == "line_drive"), 
                       speed_B ~ speed_A + vangle_A)
angle_model_ldB <- lm(data = subset(dataset, hittype == "line_drive"), speed_B ~ vangle_A)

kable(anova(partial_model_ldB,full_model_ld,test="Chisq"),format="html")
summary(full_model_ldB)$r.squared
summary(partial_model_ldB)$r.squared
summary(angle_model_ldB)$r.squared
```

Given the nested F test and the r-squared values, the full models including the interaction prove to be the best predictors of A and B. We will now fill the NAs for line drives. When the angle is less than zero for A or B, we will use the speed measurements from the non-zero system. When both angles are greater than zero, we will take the average of the speed measurements since they are more or less similar.

```{r}
dataset <- dataset %>%
  mutate(speed_A = ifelse(is.na(speed_A) & hittype == "line_drive", predict(full_model_ld), 
                          speed_A))
dataset <- dataset %>%
  mutate(speed_B = ifelse(is.na(speed_B) & hittype == "line_drive", predict(full_model_ldB), 
                          speed_B))
dataset <- dataset %>%
  mutate(true_speed = ifelse((vangle_B < 0 | vangle_A < 0) & hittype == "line_drive", NA_real_, 
                             true_speed)) %>%
  mutate(true_speed = case_when(
    hittype != "line_drive" ~ true_speed,
    hittype == "line_drive" & vangle_A < 0 ~ speed_B,
    hittype == "line_drive" & vangle_B < 0 ~ speed_A,
    hittype == "line_drive" & vangle_A >= 0 & vangle_B >= 0 ~ (speed_A + speed_B)/2,
    hittype == "line_drive" & (is.na(vangle_A) | is.na(vangle_B)) ~ (speed_A + speed_B)/2
    ))
```

## Fly balls

For fly balls, the distribution of speed and angles for A and B appeared similar. However, there were two significant fly ball `vangle_A` outliers in which the angle was negative which should not be the case for fly balls. In those two instances, we will simply use system B as the predictor of `true_speed`. Otherwise, we will average `speed_A` and `speed_B` to predict `true_speed`. We we again use linear regression to fill in the NAs for `speed_A` and `speed_B`.

```{r}
full_model_fb <- lm(data = subset(dataset, hittype == "fly_ball"), 
                    speed_A ~ speed_B + vangle_B + speed_B*vangle_B)
partial_model_fb <- lm(data = subset(dataset, hittype == "fly_ball"), 
                       speed_A ~ speed_B + vangle_B)
angle_model_fb <- lm(data = subset(dataset, hittype == "fly_ball"), speed_A ~ vangle_B)

kable(anova(partial_model_fb,full_model_fb,test="Chisq"),format="html")
summary(full_model_fb)$r.squared
summary(partial_model_fb)$r.squared
summary(angle_model_fb)$r.squared

full_model_fbB <- lm(data = subset(dataset, hittype == "fly_ball"), 
                    speed_B ~ speed_A + vangle_A + speed_A*vangle_A)
partial_model_fbB <- lm(data = subset(dataset, hittype == "fly_ball"), 
                       speed_B ~ speed_A + vangle_A)
angle_model_fbB <- lm(data = subset(dataset, hittype == "fly_ball"), speed_B ~ vangle_A)

kable(anova(partial_model_fbB,full_model_fb,test="Chisq"),format="html")
summary(full_model_fbB)$r.squared
summary(partial_model_fbB)$r.squared
summary(angle_model_fbB)$r.squared

dataset <- dataset %>%
  mutate(speed_A = ifelse(is.na(speed_A) & hittype == "fly_ball", predict(full_model_fb), 
                          speed_A))
dataset <- dataset %>%
  mutate(speed_B = ifelse(is.na(speed_B) & hittype == "fly_ball", predict(full_model_fbB), 
                          speed_B))

dataset %>%
  filter(hittype == "fly_ball" & vangle_A < 0)
dataset <- dataset %>%
  mutate(true_speed = case_when(
    hittype == "fly_ball" & vangle_A < 0 ~ speed_B,
    hittype == "fly_ball" & (vangle_A > 0 | is.na(vangle_A)) ~ (speed_A + speed_B)/2,
    hittype != "fly_ball" ~ true_speed
  ))
```

## Pop Ups

For popups, we found that `speed_A` and `speed_B` had similar distributions but `vangle_A` and `vangle_B` had very different means and distributions. Again, we should trust system A over B, so we will change `vangle_B` to `vangle_A` when possible. Though, we can still take the average of `speed_A` and `speed_B` to calculate `true_speed`. We will also use linear regression to populate the NAs for `speed_A` and `speed_B`.

```{r}
dataset <- dataset %>%
  mutate(vangle_B = case_when(
    hittype == "popup" & is.na(vangle_A) ~ vangle_B,
    hittype == "popup" & (is.na(vangle_A) == FALSE) ~ vangle_A,
    hittype != "popup" ~ vangle_B
  ))

full_model_pu <- lm(data = subset(dataset, hittype == "popup"), 
                    speed_A ~ speed_B + vangle_B + speed_B*vangle_B)
partial_model_pu <- lm(data = subset(dataset, hittype == "popup"), 
                       speed_A ~ speed_B + vangle_B)
angle_model_pu <- lm(data = subset(dataset, hittype == "popup"), speed_A ~ vangle_B)

kable(anova(partial_model_pu,full_model_pu,test="Chisq"),format="html")
summary(full_model_pu)$r.squared
summary(partial_model_pu)$r.squared
summary(angle_model_pu)$r.squared

full_model_puB <- lm(data = subset(dataset, hittype == "popup"), 
                    speed_B ~ speed_A + vangle_A + speed_A*vangle_A)
partial_model_puB <- lm(data = subset(dataset, hittype == "popup"), 
                       speed_B ~ speed_A + vangle_A)
angle_model_puB <- lm(data = subset(dataset, hittype == "popup"), speed_B ~ vangle_A)

kable(anova(partial_model_fbB,full_model_fb,test="Chisq"),format="html")
summary(full_model_puB)$r.squared
summary(partial_model_puB)$r.squared
summary(angle_model_puB)$r.squared

dataset <- dataset %>%
  mutate(speed_A = ifelse(is.na(speed_A) & hittype == "popup", predict(full_model_pu), 
                          speed_A))
dataset <- dataset %>%
  mutate(speed_B = ifelse(is.na(speed_B) & hittype == "popup", predict(full_model_puB), 
                          speed_B))

dataset <- dataset %>%
  mutate(true_speed = case_when(
    hittype == "popup" ~ (speed_A + speed_B)/2,
    hittype != "popup" ~ true_speed
  ))
```

# Conclusion

First, let's look at the 5-number summary of the calculated `true_speed`:

```{r}
dataset %>%
  filter(hittype == "ground_ball") %>%
  summarise(mingb = min(true_speed, na.rm = TRUE), q1gb = quantile(true_speed, 0.25, na.rm = 
                                                                     TRUE), 
            meangb = mean(true_speed, na.rm = TRUE), q3gb = quantile(true_speed, 0.75, na.rm = 
                                                                      TRUE),
            maxgb = max(true_speed, na.rm = TRUE))
dataset %>%
  filter(hittype == "line_drive") %>%
  summarise(minld = min(true_speed, na.rm = TRUE), q1ld = quantile(true_speed, 0.25, na.rm = 
                                                                     TRUE), 
            meanld = mean(true_speed, na.rm = TRUE), q3ld = quantile(true_speed, 0.75, na.rm = 
                                                                      TRUE),
            maxld = max(true_speed, na.rm = TRUE))
dataset %>%
  filter(hittype == "fly_ball") %>%
  summarise(minfb = min(true_speed, na.rm = TRUE), q1fb = quantile(true_speed, 0.25, na.rm = 
                                                                     TRUE), 
            meanfb = mean(true_speed, na.rm = TRUE), q3fb = quantile(true_speed, 0.75, na.rm = 
                                                                      TRUE),
            maxfb = max(true_speed, na.rm = TRUE))
dataset %>%
  filter(hittype == "popup") %>%
  summarise(minpu = min(true_speed, na.rm = TRUE), q1pu = quantile(true_speed, 0.25, na.rm = 
                                                                     TRUE), 
            meanpu = mean(true_speed, na.rm = TRUE), q3pu = quantile(true_speed, 0.75, na.rm = 
                                                                      TRUE),
            maxpu = max(true_speed, na.rm = TRUE))
```

For each hit type, the distributions seem to be distinctly different, thus validating the idea that each hit type should be treated independently. It is intuitive that popups would have the lowest mean `true_speed`, as they do not leave the infield. Moreover, it makes sense that line drives would have the highest mean `true_speed`, since they are hit squarely.

In all, to predict batter performance next year, we recommend the following:

For ground balls: Use system A to measure the speed, and if A is unavailable, then use a linear regression model to predict A from B. This is because there is a large discrepancy between A and B, and we are told that system A is generally more reliable.

For line drives: Disregard any observations in which `vangle_A` and `vangle_B` are both negative, as that does not align with the characteristics of a line drive. Then, average `speed_A` and `speed_B` to calculate `true_speed` since the measurements appear similar. If A or B is NA, then use linear regression with the known system to predict the other and average them.

For fly balls: Remove significant `vangle_A` outliers, as system A seems to occasionally malfunction in regards to angles of fly balls. In those cases, resort to using system B. Otherwise, average the speeds of systems A and B due to the fact that they are similar.

For popups: Replace `vangle_B` with `vangle_A` because they are drastically different, and we must assume A is more reliable. For speed, A and B seem to be consistent so take the average speed.

This `true_speed` system should prove to be a relatively accurate way of measuring hit speed.
